Viscous Transport in Eroding Porous Media

### 2019-06-09 docs/transport/erosion_transport.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}
{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid. The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$. Let the initial radius of the body be $r$, the initial length of the body be $L$, 
and $d$ be the minimum initial distance from body to wall. Let $N_\out$ and $N_\iin$ be the number of discretization points on the outer wall and discretization points on the bodies, respectively.  We fix $N_\out=1024$ for all the simultions. We impose the fixed pressure drop condition on our numerical results to satisfy the physical phenomenon which has been introduced in~\cite{qua-moo2018}. We use smoothing parameters of $\eps$ and $\sigma$ to control eroding motion on the bodies and the parameters $\alpha_1$ and $\alpha_2$ to determine if the target point is close enough to boundary.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and $\eps = 15/256$ and $\sigma=10/256$.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in the shear flow. 
This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
The initial velocity of flow from the left side of $\Omega$ is 
$$\UU(\xx)=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
We place a single eroding body close to the no-slip wall ($y=-1$).
This example has no pressure drop. 
We investigate the shape of eroding body when it is close to a solid wall at the three  
distances $d=h, h/2$, and $ h/10$ where $h=L/N_\iin$ is the arclength spacing correponding to the initial radius $r$ of 0.4 and $N_\iin=256$ discretization points .

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this section, we present the numerical simulations of dense packings
of eroding bodies.  The computational domain $\Omega$ is a rectangle
$[-3,3] \times [-1,1]$ with rounded off corners and we place bodies only
in $[-1,1] \times [-1,1]$.  For all simulations, we discretize $\Gamma =
\bd \Omega$ with $N_\out=1024$ points.  The Dirichlet boundary condition
on $\Gamma$ is a Hagen-Poiseuille flow.  As the bodies erode, the flow
rate is adjusted to maintain the physical constant pressure drop
boundary condition.  To maintain this pressure drop, we compute the
pressure at near the inlet and outlet at each time step as described in
our previous work~\cite{qua-moo2018}.

The initial shape of the eroding body $\gamma_i$ is a circle centered at
$\cc_i$ with radius $r_i$ and length $L_i = 2\pi r_i$, and each
$\gamma_i$ is discretized with $N_\iin$ points.  Using the annealing
algorithm described in Section ???, the initial configuration has the
desired initial porosity, and the minimum separation between any pair of
bodies and between the bodies and solid wall is $d$.  A no-slip boundary
condition is imposed on $\gamma$.  To round off inevitable corners on
the eroding bodies, we apply smoothing the smoothing parameters
$\eps=???$ and $\sigma=???$, as described in~\cite{qua-moo2018}, for all
simulations.

Finally, the parameters used to determine if a point uses the trapezoid
or Barycentric quadrature rule are $\alpha_\iin = ???$ and
$\alpha_\out=???$.

\todo[inline]{time step size}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, a time-step of $\Dt=10^{-4}$, and $\eps = 15/256$ and $\sigma=10/256$.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in the shear flow. 
This example shows that we can resolve eroding bodies near the solid wall which is similar to \cite{mit-spa2017}.
The initial velocity of flow from the left side of $\Omega$ is 
$$\UU(\xx)=\begin{bmatrix} y+1 \\ 0 \end{bmatrix}.$$
We place a single eroding body close to the no-slip wall ($y=-1$).
This example has no pressure drop. 
We investigate the shape of eroding body when it is close to a solid wall at the three  
distances $d=h, h/2$, and $ h/10$ where $h=L/N_\iin$ is the arclength spacing correponding to the initial radius $r$ of 0.4 and $N_\iin=256$ discretization points .
